The Next Generation of Canadian Salmon

### 2024-04-19 output/paper.qmd
update overviews

---
title: "The Next Generation of Canadian Salmon"
subtitle: "The Effects of the Commercial Fishing Industry on Spawning Rates"
author: 
  - Timothius Prajogi
thanks: "Code and data are available at: https://github.com/prajogt/canadian_salmon_spawn.git ."
date: today
date-format: long
abstract: "Using the NuSEDS dataset and Catch Estimates for the Pacific Region Commerical Salmon Fishery dataset provided by the Government of Canada, we investigate the effects of commercial fishing on the reproductive capacity of Canadian Salmon. Along with that, we investigate how much of the change in spawn rates can be attributed to the health of the ecosystem, climate, and the fish that live in it. This paper discusses the impact of direct human intervention in the form of commercial fishing, aiming to highlight the importance in proper management and control in the fishing industry in alignement with changes in the environment by predicting spawning trends of future generations."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
header-includes:
  \usepackage{placeins}
---

>>>>

---
title: "The Next Generation of Canadian Salmon"
subtitle: "The Effects of the Commercial Fishing Industry on Spawning Rates"
author: 
  - Timothius Prajogi
thanks: "Code and data are available at: https://github.com/prajogt/canadian_salmon_spawn.git ."
date: today
date-format: long
abstract: "Using the NuSEDS dataset and Catch Estimates for the Pacific Region Commerical Salmon Fishery dataset provided by the Government of Canada, we investigate the effects of commercial fishing on the reproductive capacity of Canadian Salmon. Along with that, we can infer how much of the change in spawn rates can be therefore attributed to the health of the ecosystem, climate, and the fish that live in it. This paper discusses the impact of direct human intervention in the form of commercial fishing, aiming to highlight the importance in proper management and control in the fishing industry in alignement with changes in the environment by predicting spawning trends of future generations."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
header-includes:
  \usepackage{placeins}
---
